Figures

### 2025-03-20 docs/_tex/index.tex
fix html table in index.

\begin{tabular}{l c c}
\hline
 & Confidence in AZ Elections & w/Interaction \\
\hline
(Intercept)                & $0.03 \; (0.08)$        & $0.07 \; (0.08)$        \\
Treatment                  & $0.18 \; (0.05)^{***}$  & $0.09 \; (0.06)$        \\
Not Legitimate             & $-0.72 \; (0.07)^{***}$ & $-0.86 \; (0.09)^{***}$ \\
Republican                 & $0.11 \; (0.08)$        & $0.12 \; (0.08)$        \\
Democrat                   & $0.17 \; (0.09)$        & $0.17 \; (0.09)^{*}$    \\
Not Legitimate * Treatment &                         & $0.27 \; (0.11)^{*}$    \\
\hline
R$^2$                      & $0.14$                  & $0.14$                  \\
Adj. R$^2$                 & $0.13$                  & $0.14$                  \\
Num. obs.                  & $1263$                  & $1263$                  \\
\hline
\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
\end{tabular}

@@

The first model in Table \ref{tbl-legit} shows that overall confidence
in elections among those who read the treatment vignette was
significantly (statistically) greater than those who read the control,
on average and netting out the effects of partisanship and legitimacy
beliefs. Democratic partisanship remains marginally significant at
\(90\%\) confidence level (\(p = 0.055\)). Not believing the 2020
election of Joe Biden was legitimate is negatively associated with
confidence in elections. In order to assess the magnitude of this
interaction effect of the treatment on those who refuted the 2020
election results, I ran a model where confidence in elections was
regressed on the interaction between the treatment and legitimacy
beliefs, controlling for partisanship.

@@

\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
width={0.8\linewidth},
colspec={X[]X[]X[]},
column{1,2,3}={}{font=\fontsize{0.8em}{1.1em}\selectfont,},
hline{27}={1,2,3}{solid, black, 0.1em},
}                     %% tabularray inner close
\toprule
& \textbf{log(OR)} & \textbf{95\% CI} \\ \midrule %% TinyTableHeader
\textbf{Age} &  &  \\
18-34 &  &  \\
35-54 & -0.17 & -0.45, 0.12 \\
55-74 & -0.15 & -0.46, 0.15 \\
75-85+ & 0.40 & -0.15, 0.97 \\
\textbf{Gender} &  &  \\
Male &  &  \\
Female & -0.07 & -0.29, 0.15 \\
Other/Refused & -0.62 & -1.8, 0.42 \\
\textbf{Race/Ethnicity} &  &  \\
White &  &  \\
Asian & 0.03 & -0.55, 0.60 \\
Black & -0.08 & -0.43, 0.27 \\
Other & 0.05 & -0.82, 0.93 \\
Hispanic & -0.24 & -0.86, 0.38 \\
American Indian & 0.50 & -0.58, 1.7 \\
\textbf{Education} &  &  \\
H.S. or less &  &  \\
Some college no degree & -0.10 & -0.42, 0.21 \\
College degree & -0.16 & -0.45, 0.12 \\
Postgraduate degree & 0.02 & -0.35, 0.40 \\
\textbf{Party ID} &  &  \\
Independent &  &  \\
Republican & 0.12 & -0.24, 0.48 \\
Democrat & 0.05 & -0.31, 0.40 \\
Num.Obs & 1268 &  \\
Log.Lik & -873.349 &  \\
DF & 15 &  \\
\(\chi^2\) & 11.01 &  \\
\(P(>\chi^2)\) & 0.752 &  \\
Deviance & 1746.698 &  \\
Null Deviance & 1757.708 &  \\
\bottomrule
\end{tblr}

>>>>

\centering
\begin{talltblr}[         %% tabularray outer open
entry=none,label=none,
note{}={{\fontsize{0.75em}{0.75em}\selectfont Outcome variable mean-centered and scaled by 1 standard deviation}},
note{ }={{\fontsize{0.75em}{0.75em}\selectfont + p < 0.1, * p < 0.05, ** p < 0.01, *** p < 0.001}},
]                     %% tabularray outer close
{                     %% tabularray inner open
width={0.8\linewidth},
colspec={X[]X[]X[]},
column{2,3}={}{halign=c, font=\fontsize{0.8em}{1.1em}\selectfont, halign=c,},
column{1}={}{halign=l, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
hline{7}={1,2,3}{solid, black, 0.1em},
}                     %% tabularray inner close
\toprule
& Confidence in AZ Elections & w/Interaction \\ \midrule %% TinyTableHeader
(Intercept) & \num{0.03} (\num{0.08}) & \num{0.07} (\num{0.08}) \\
Treatment & \num{0.18} (\num{0.05})*** & \num{0.09} (\num{0.06}) \\
Not Legitimate & \num{-0.72} (\num{0.07})*** & \num{-0.86} (\num{0.09})*** \\
Republican & \num{0.11} (\num{0.08}) & \num{0.12} (\num{0.08}) \\
Democrat & \num{0.17} (\num{0.09})+ & \num{0.17} (\num{0.09})* \\
Treatment:Not Legitimate &  & \num{0.27} (\num{0.11})* \\
Num.Obs. & \num{1263} & \num{1263} \\
R2 Adj. & \num{0.134} & \num{0.138} \\
\bottomrule
\end{talltblr}

@@

The first model in Table~\ref{tbl-legit} shows that overall confidence
in elections among those who read the treatment vignette was
significantly (statistically) greater than those who read the control,
on average and netting out the effects of partisanship and legitimacy
beliefs. Democratic partisanship remains marginally significant at
\(90\%\) confidence level (\(p = 0.055\)). Not believing the 2020
election of Joe Biden was legitimate is negatively associated with
confidence in elections. In order to assess the magnitude of this
interaction effect of the treatment on those who refuted the 2020
election results, I ran a model where confidence in elections was
regressed on the interaction between the treatment and legitimacy
beliefs, controlling for partisanship.

@@

\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
width={0.8\linewidth},
colspec={X[]X[]X[]},
column{1,2,3}={}{font=\fontsize{0.8em}{1.1em}\selectfont,},
hline{27}={1,2,3}{solid, black, 0.1em},
}                     %% tabularray inner close
\toprule
& \textbf{log(OR)} & \textbf{95\% CI} \\ \midrule %% TinyTableHeader
\textbf{Age} &  &  \\
18-34 &  &  \\
35-54 & -0.17 & -0.45, 0.12 \\
55-74 & -0.15 & -0.46, 0.15 \\
75-85+ & 0.40 & -0.15, 0.97 \\
\textbf{Gender} &  &  \\
Male &  &  \\
Female & -0.07 & -0.29, 0.15 \\
Other/Refused & -0.62 & -1.8, 0.42 \\
\textbf{Race/Ethnicity} &  &  \\
White &  &  \\
Asian & 0.03 & -0.55, 0.60 \\
Black & -0.08 & -0.43, 0.27 \\
Other & 0.05 & -0.82, 0.93 \\
Hispanic & -0.24 & -0.86, 0.38 \\
American Indian & 0.50 & -0.58, 1.7 \\
\textbf{Education} &  &  \\
H.S. or less &  &  \\
Some college no degree & -0.10 & -0.42, 0.21 \\
College degree & -0.16 & -0.45, 0.12 \\
Postgraduate degree & 0.02 & -0.35, 0.40 \\
\textbf{Party ID} &  &  \\
Independent &  &  \\
Republican & 0.12 & -0.24, 0.48 \\
Democrat & 0.05 & -0.31, 0.40 \\
Num.Obs & 1268 &  \\
Log.Lik & -873.349 &  \\
DF & 15 &  \\
\(chisq\) & 11.01 &  \\
\(P(>chisq)\) & 0.752 &  \\
Deviance & 1746.698 &  \\
Null Deviance & 1757.708 &  \\
\bottomrule
\end{tblr}

### 2025-03-20 index.qmd
fix html table in index.

::: {.content-visible when-format="html" unless-format="pdf"}

```{r}
#| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
#| tbl-pos: H

@@

texreg::htmlreg(
  list(m1, m2), 
  single.row = T,
  caption.above = T,
  custom.model.names = c("Confidence in AZ Elections", "w/Interaction"),
  custom.coef.names = c(
    "(Intercept)",
    "Treatment",
    "Not Legitimate",
    "Republican",
    "Democrat",
    "Not Legitimate * Treatment"
    )
)

@@

:::

::: {.content-visible when-format="pdf" unless-format="html"}

```{r}
#| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
#| tbl-pos: H
#| label: tbl-legit
#| results: asis

texreg::texreg(
  list(m1, m2),
  single.row = T,
  caption = NULL,
  caption.above = T,
  use.packages = F,
  table = F, # set `table = FALSE`. Quarto handles table cross-ref env
  custom.model.names = c("Confidence in AZ Elections", "w/Interaction"),
  custom.coef.names = c(
    "(Intercept)",
    "Treatment",
    "Not Legitimate",
    "Republican",
    "Democrat",
    "Not Legitimate * Treatment"
    )
)

:::

The first model in Table \ref{tbl-legit} shows that overall confidence in elections among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs. Democratic partisanship remains marginally significant at $90\%$ confidence level ($p = 0.055$). Not believing the 2020 election of Joe Biden was legitimate is negatively associated with confidence in elections. In order to assess the magnitude of this interaction effect of the treatment on those who refuted the 2020 election results, I ran a model where confidence in elections was regressed on the interaction between the treatment and legitimacy beliefs, controlling for partisanship.

@@

# create 2nd table containing only logit model fit statistics
# using custom function, get logit regression model fit stats... 
gof_stats <- lrm.gof.stats(m1) |> 
  # omit certain stats (saves space)
  dplyr::select(
    nobs, logLik, df, chisq, P..chi., deviance, null.deviance,
    -AIC, -BIC, -df.null, -df.residual) |> 
  # rename column variables
  dplyr::rename(
    "Num.Obs"       = "nobs",
    "Null Deviance" = "null.deviance",
    "Deviance"      = "deviance",
    "DF"            = "df",
    "Log.Lik"       = "logLik",
    "\\chi^2"       = "chisq",
    "P(>\\chi^2)"   = "P..chi."
  ) |> 
  # pivot into two column long-form dataframe
  tidyr::pivot_longer(cols = everything(),names_to = " ", values_to = '**log(OR)**') |>
  # pipe into tinytable
  tinytable::tt(width = 0.8) |> 
  # ensure rows with math text are identified and formatted as math (i.e., $..$)
  tinytable::format_tt(i = c(4,5), j = 1, math = T)

>>>>

```{r}
#| label: tbl-legit
#| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
#| tbl-pos: H

@@

tab_legit <- modelsummary::modelsummary(
  models = list(m1, m2), fmt = 2,
  estimate = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  stars = T,
  coef_rename = c(
    "(Intercept)"                        = "(Intercept)",
    "groupTreatment"                     = "Treatment",
    "q7Not legitimate"                   = "Not Legitimate",
    "partyid_3catRepublican"             = "Republican",
    "partyid_3catDemocrat"               = "Democrat",
    "groupTreatment x q7Not legitimate"  = "Not Legitimate * Treatment"),
  gof_map = c("nobs", "r2", "adj.r.squared"),
  notes = list(
    "Outcome variable mean-centered and scaled by 1 standard deviation",
    "+ p < 0.1, * p < 0.05, ** p < 0.01, *** p < 0.001"),
  width = 0.8
)

colnames(tab_legit) <- c(" ", "Confidence in AZ Elections", "w/Interaction")

tab_legit |> 
  tinytable::style_tt(
    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
    align = "lcc"
    ) |>  
  tinytable::style_tt(i = 6, line = "t") |> 
  tinytable::style_tt(i = "notes", fontsize = 0.75)

@@

The first model in @tbl-legit shows that overall confidence in elections among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs. Democratic partisanship remains marginally significant at $90\%$ confidence level ($p = 0.055$). Not believing the 2020 election of Joe Biden was legitimate is negatively associated with confidence in elections. In order to assess the magnitude of this interaction effect of the treatment on those who refuted the 2020 election results, I ran a model where confidence in elections was regressed on the interaction between the treatment and legitimacy beliefs, controlling for partisanship.

@@

# create 2nd table containing only logit model fit statistics
# using custom function, get logit regression model fit stats... 
gof_stats <- lrm.gof.stats(m1) |> 
  # omit certain stats (saves space)
  dplyr::select(
    nobs, logLik, df, chisq, P..chi., deviance, null.deviance,
    -AIC, -BIC, -df.null, -df.residual) |> 
  # rename column variables
  dplyr::rename(
    "Num.Obs"       = "nobs",
    "Null Deviance" = "null.deviance",
    "Deviance"      = "deviance",
    "DF"            = "df",
    "Log.Lik"       = "logLik",
    "chisq"       = "chisq",
    "P(>chisq)"   = "P..chi."
  ) |> 
  # pivot into two column long-form dataframe
  tidyr::pivot_longer(cols = everything(),names_to = " ", values_to = '**log(OR)**') |>
  # pipe into tinytable
  tinytable::tt(width = 0.8) |> 
  # ensure rows with math text are identified and formatted as math (i.e., $..$)
  tinytable::format_tt(i = c(4,5), j = 1, math = T)

### 2025-03-20 notebooks/figures.qmd
clean repo and push to publish
fix html table in index.

---
title: "Figures"
execute:
  enabled: true
---

@@

# plot of distrust in AZ elections by educational attainment :::::::: 
distrust.az.educ.likert <- data |> 
  filter(!is.na(educ_4cat)) |> 
  mutate(
    educ_3cat = pewmethods::fct_case_when(
      educ_4cat %in% c("H.S. or less") ~ "H.S. or less",
      educ_4cat %in% c("Some college no degree") ~ "Some college no Degree",
      educ_4cat %in% c("Postgraduate degree", "College degree") ~ "College Graduate")
    ) |>  
  likert_plot(x = all_of(distrust.az.items), y = 'educ_3cat', facet_rows=vars(.question),
              facet_label_wrap = 15, variable_labels = distrust.az.varlabels,
              subtitle = "Maricopa County, AZ")
```

@@

```{r}
#| label: fig-patch5

p5.distrust.az.educ <- distrust.az.educ.likert + distrust.lcl.educ.likert +
    patchwork::plot_layout(guides = "collect") & 
    theme(legend.position = "bottom")

@@

```{r}
#| label: fig-patch6

p6.trust.az.gender <- trust.az.gender.likert / distrust.az.gender.likert +
  patchwork::plot_annotation(
    caption = str_wrap(
      "Gender Non-binary (n=7) and those who preferred not to say (n=9) response categories omitted for lack of observations. Missing values omitted (n=15)",
      width = 150
    ),
    theme = theme(text = element_text(family = "Palatino Linotype"))
  ) +
  patchwork::plot_layout(guides = 'keep') &
  theme(legend.position = "bottom")

@@

```{r}
#| label: fig-p13

@@

```{r}
#| label: fig-patch7

p7.trust.lcl.gender <- trust.lcl.gender.likert/distrust.lcl.gender.likert+
  patchwork::plot_annotation(
    caption = str_wrap("Gender Non-binary (n=7) and those who preferred not to say (n=9) response categories omitted for lack of observations. Missing values omitted (n=15)",
                       width = 150), 
    theme = theme(text = element_text(family = "Palatino Linotype")))+
    patchwork::plot_layout(guides = 'keep') & 
    theme(legend.position = "bottom")
```

@@

```{r}
#| label: fig-patch8

p8.trust.az.party <- trust.az.party.likert/distrust.az.party.likert+
    patchwork::plot_layout(guides = 'keep') & 
    theme(legend.position = "bottom")

@@

```{r}
#| label: fig-patch9

p9.trust.lcl.party <- trust.lcl.party.likert/distrust.lcl.party.likert+
    patchwork::plot_layout(guides = 'keep') & 
    theme(legend.position = "bottom")

@@

trust.likert.treat.az

@@

trust.likert.treat.lcl

@@

```{r}
#| label: fig-patch10
#| fig-cap: "Trust in Election Administration by Experiment Condition"
#| fig-height: 4.5
#| fig-pos: "h"

@@

# plot of trust in AZ elections by experiment condition and party id
trust.az.treat.partyid <- data |> 
  filter(!is.na(partyid_3cat)) |>
  likert_plot(
    x = all_of(trust.az.items),
    y = 'partyid_3cat',
    facet_rows = vars(.question),
    facet_cols = vars(group),
    facet_label_wrap = 15,
    variable_labels = trust.az.varlabels,
    title = "Trust in Maricopa County, AZ Elections by Treatment and Partisanship")
```

@@

# plot of trust in local elections by experiment condition and party id
trust.lcl.treat.partyid <- data |> 
  filter(!is.na(partyid_3cat)) |>
  likert_plot(
    x = all_of(trust.lcl.items),
    y = 'partyid_3cat',
    facet_rows = vars(.question),
    facet_cols = vars(group),
    facet_label_wrap = 15,
    variable_labels = trust.lcl.varlabels,
    title = "Trust in Local Area Elections by Treatment and Partisanship")
```

```{r}
#| label: fig-patch12

@@

```{r}
#| label: fig-patch15
#| fig-height: 4.5
#| fig-width: 8

>>>>

---
title: "Figures"
execute:
  enabled: true
  warning: false
---

@@

# plot of distrust in AZ elections by educational attainment :::::::: 
distrust.az.educ.likert <- data |> 
  filter(!is.na(educ_4cat)) |> 
  mutate(
    educ_3cat = pewmethods::fct_case_when(
      educ_4cat %in% c("H.S. or less") ~ "H.S. or less",
      educ_4cat %in% c("Some college no degree") ~ "Some college no Degree",
      educ_4cat %in% c("Postgraduate degree", "College degree") ~ "College Graduate")
    ) |>  
  likert_plot(x = all_of(distrust.az.items), y = 'educ_3cat', facet_rows=vars(.question),
              facet_label_wrap = 15, variable_labels = distrust.az.varlabels,
              subtitle = "Maricopa County, AZ")

@@

```{r}
#| label: fig-patch5
#| fig-cap: "Distrust by Educational Attainment"
#| fig-width: 8
#| column: body-outset

p5.distrust.az.educ <- distrust.az.educ.likert + distrust.lcl.educ.likert +
    patchwork::plot_layout(guides = "collect", axes = "collect") & 
    theme(legend.position = "bottom")

@@

```{r}
#| label: fig-patch6
#| fig-cap: "Trust in Maricopa County, AZ Elections by Gender"
#| fig-height: 8

p6.trust.az.gender <- (trust.az.gender.likert + distrust.az.gender.likert) +
  patchwork::plot_annotation(
    caption = str_wrap(
      "Gender Non-binary (n=7) and those who preferred not to say (n=9) response categories omitted for lack of observations. Missing values omitted (n=15)",
      width = 80
    ),
    theme = theme(text = element_text(family = "TeX Gyre Pagella"))
  ) +
  patchwork::plot_layout(
    ncol = 1, 
    nrow = 2,
    guides = 'keep', axes = "collect") &
  theme(legend.position = "bottom")

@@

```{r}
#| label: fig-p13
#| warning: false
#| message: false

@@

```{r}
#| label: fig-patch7
#| fig-cap: "Trust in Local Area Elections by Gender"
#| fig-height: 8

p7.trust.lcl.gender <- trust.lcl.gender.likert/distrust.lcl.gender.likert+
  patchwork::plot_annotation(
    caption = str_wrap("Gender Non-binary (n=7) and those who preferred not to say (n=9) response categories omitted for lack of observations. Missing values omitted (n=15)",
                       width = 80), 
    theme = theme(text = element_text(family = "TeX Gyre Pagella"))) +
  patchwork::plot_layout(guides = 'keep', axes = "collect") &
  theme(legend.position = "bottom")

p7.trust.lcl.gender

@@

```{r}
#| label: fig-patch8
#| fig-height: 8

p8.trust.az.party <- trust.az.party.likert/distrust.az.party.likert +
  patchwork::plot_layout(guides = 'keep', axes = "collect") &
  theme(legend.position = "bottom")

@@

```{r}
#| label: fig-patch9
#| fig-height: 8

p9.trust.lcl.party <- trust.lcl.party.likert/distrust.lcl.party.likert+
  patchwork::plot_layout(guides = 'keep', axes = "collect") &
  theme(legend.position = "bottom")

@@

@@

@@

```{r}
#| label: fig-patch10
#| fig-cap: "Trust in Election Administration by Experiment Condition"
#| fig-height: 4.5
#| fig-width: 8
#| fig-pos: "h"

@@

# plot of trust in AZ elections by experiment condition and party id
trust.az.treat.partyid <- data |> 
  filter(!is.na(partyid_3cat)) |>
  likert_plot(
    x = all_of(trust.az.items),
    y = 'partyid_3cat',
    facet_rows = vars(.question),
    facet_cols = vars(group),
    facet_label_wrap = 15,
    variable_labels = trust.az.varlabels,
    subtitle = "Maricopa County, AZ")
```

@@

# plot of trust in local elections by experiment condition and party id
trust.lcl.treat.partyid <- data |> 
  filter(!is.na(partyid_3cat)) |>
  likert_plot(
    x = all_of(trust.lcl.items),
    y = 'partyid_3cat',
    facet_rows = vars(.question),
    facet_cols = vars(group),
    facet_label_wrap = 15,
    variable_labels = trust.lcl.varlabels,
    subtitle = "Local Area")
```

```{r}
#| label: fig-patch12
#| fig-cap: "Trust in Elections by Treatment and Partisanship"
#| fig-height: 8

@@

```{r}
#| label: fig-patch15
#| fig-height: 5.5
#| fig-width: 8
